---
title: "machineRead_rfp"
output: html_document
date: '2022-12-28'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyverse)
library(pdftools)
library(tesseract)
library(stringr)

# might be needed for some tasks
#library(readtext)
#library(quanteda)
#library(stringi)

eng <- tesseract("eng")
```

*Overall end goal*: Want to produce a dataset/spreadsheet for each RFP. Rows as paragraphs that include PEA language, column 1 has the paragraph & column 2 has the thing that is PEA language

## The function

Make dataframe where para is row and cols for page number and paragraph number. Then a col for "PEA citation".

```{r}
## chris: note: should have made a few functions and has this bigger function use those, but was lazy.

# one big function that does everything
rfa.fun <- function(n=5)
{
  # scan in pdf
  text <- pdf_text(paste0(getwd(),"/RFPs_2022-12-28/",files[n]))
  
  #make df of rows as paragraphs, cols for text, page num, etc
  test <- as.data.frame(text, col.names="text")
  test$page <- row.names(test)
  fill_df <- test %>% separate_rows(text, sep="\n\n")
  fill_df <- fill_df %>% group_by(page) %>%
    mutate(para_of_page = row_number())
  fill_df$paragraph_num <- row.names(fill_df)
  rm(test); rm(text)
  
  #clean
  fill_df$text <- str_squish(fill_df$text)
  df <- fill_df
  
  # look for keywords
  keyWords1 <- c("Political economy analysis", "Political economy", 
              "Thinking and working politically")
  keyWords2 <- c("PEA","TWP")
  keyWords <- c(keyWords1, keyWords2)
  
  df$pea_01 <- ifelse(grepl(paste(keyWords1, collapse="|"),
                                 df$text,ignore.case=T), 1, 0)
  df$pea_01 <- ifelse(grepl(paste(keyWords2, collapse="|"),
                                 df$text), 1, df$pea_01)
  
  #stop if no keywords
  if(sum(df$pea_01)>0)
  {
    # Dump pages with no keywords
  pages <- unique(df$page[df$pea_01 %in% 1])
  df <- df[df$page %in% pages,]
  
  # next, which words are used?
  df[,keyWords] <- NA
  for(i in 1:length(keyWords))
  {
    df[,keyWords[i]] <- ifelse(grepl(keyWords[i], df$text, ignore.case=T), 1, 0)
  }
  
  # make a single column showing all the words used
  ## here, col 6 starts the pea words
  df$all_pea_words <- apply(df[,6:ncol(df)], 1, function(x) paste(colnames(df[,6:ncol(df)])[which(x == 1)], collapse = ", "))
  
  # remove cols for individual words
  df <- df[,c(1:5,ncol(df))]
  
  # save csv
  write.csv(df, file=paste0("rfp_2022_sheets/",gsub(".pdf", "", files[n]), "_sheet.csv"), row.names = FALSE)
  }
  
}
#test <- rfa.fun(n=145)
```


## scan in docs & loop function over each of them

```{r}
files <- list.files(path=paste0(getwd(),"/RFPs_2022-12-28"),
                    pattern=".pdf", 
                    all.files=FALSE, full.names=FALSE)
stopifnot(length(files)==380)

system.time(for(i in 1:length(files))
{
  rfa.fun(i)
})

#how many sheets?
end <- list.files(path=paste0(getwd(),"/rfp_2022_sheets"),
                   pattern=".csv")
length(end)
```

# upload to googledrive

Cannot link gmail account to usaid googledrive.  Must manually upload.
